PANCHANGE_data_preprocessing

### 2020-11-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
Knitted NBR for preprocessing script and GLAD for same script (new html produced)

# Specify cohort
```{r Specify cohort}
GLAD = FALSE
EDGI = FALSE
NBR = TRUE
RAMP = FALSE
GLAD_and_EDGI = FALSE
```

@@

## GLAD and EDGI
### Create data frame 
```{r GLAD and EDGI combined}
glad.and.edgi.dem.raw.id <- rbind(glad.dem.raw.id, edgi.dem.raw.id)
```

>>>>

# Specify cohort
```{r Specify cohort}
GLAD = TRUE
EDGI = FALSE
NBR = FALSE
RAMP = FALSE
GLAD_and_EDGI = FALSE
```

@@

## GLAD and EDGI
### Create data frame 
```{r GLAD and EDGI combined}
if(GLAD_and_EDGI == TRUE){
glad.and.edgi.dem.raw.id <- rbind(glad.dem.raw.id, edgi.dem.raw.id)
}
```
